Self-similarity of the elements of the feasible set

### 2020-11-30 analysis/reports/accessory/old_reports/cross_dataset.Rmd
tidying and sending docs to SKME

>>>>

```{r nyears in mcdb}

mcdb_di <- filter(all_di, dat == "mcdb")

mcdb_sites <- read.csv(here::here("working-data/site_data/mammal_community_db_sites.csv"), stringsAsFactors = F)

mcdb_sites <- mcdb_sites %>%
  select(site_id, n_years, study_duration) %>%
  rename(site = site_id) %>%
  mutate(site = as.character(site))

mcdb_di <- left_join(mcdb_di, mcdb_sites, by = "site")

nyears_hist <- ggplot(data = distinct(select(mcdb_di, site, n_years)), aes(x = n_years)) +
  geom_histogram(pad = T, boundary = 0) +
  theme_bw() +
  ggtitle("Nyears in MCDB")

nyears_hist
# 
# duration_hist <-  ggplot(data = distinct(select(mcdb_di, site, study_duration)), aes(x = study_duration)) +
#   geom_histogram(pad = T, boundary = 0) +
#   theme_bw() +
#   ggtitle("Duration in MCDB")
# 
# duration_hist

nyears_skew <- ggplot(data = mcdb_di, aes(x = n_years, y = skew_percentile)) +
  geom_point(alpha = .2) +
  #facet_wrap(vars(singletons)) +
  theme_bw() +
  ggtitle("Skew v nyears (MCDB)")

nyears_skew

nyears_simpson <- ggplot(data = mcdb_di, aes(x = n_years, y = simpson_percentile)) +
  geom_point(alpha = .2) +
  #facet_wrap(vars(singletons)) +
  theme_bw() +
  ggtitle("Simpson v nyears (MCDB)")

nyears_simpson
```

### 2020-11-30 analysis/reports/self_similarity.Rmd
remove dataset level reports from pipelines
tidying and sending docs to SKME

---
title: "Self-similarity of the elements of the feasible set"
author: Renata Diaz
date: "`r Sys.Date()`"
output: 
    github_document:
       df_print: kable
---

@@

### Directly establishing self-similarity

#### Overview

@@

#### Walkthrough

@@

### Across a range of S and N

@@

#### Heat maps

@@

##### R2

@@

##### R2 on logged vectors

@@

##### Coefficient of determination

@@

##### Proportion of individuals allocated to different species

@@

##### K-L divergence

@@

Here is div for only "small" feasible sets (those with fewer than `r exp(20)` elements in the feasible set). This lets us zoom in on the distributions where they start to broaden out.

@@

>>>>

---
title: "Self-similarity of the elements of the feasible set"
author: Renata Diaz
date: "`r Sys.Date()`"
output: 
    word_document:
       df_print: kable
---

@@

## Directly establishing self-similarity

### Overview

@@

### Walkthrough

@@

## Across a range of S and N

@@

### Heat maps

@@

#### R2

@@

#### R2 on logged vectors

@@

#### Coefficient of determination

@@

#### Proportion of individuals allocated to different species

@@

#### K-L divergence

@@

Here is K-L divergence for only "small" feasible sets (those with fewer than `r exp(20)` elements in the feasible set). This lets us zoom in on the distributions where they start to broaden out.

@@

### In summary

Large feasible sets are consistently more self-similar than small ones.
